---
title: "BEH1_indiv_setup"
author: "Leonardo Sutandi"
date: "2025-03-18"
output: html_document
---


This script combines 5 blocks to 1 data set for each participant (change info in "Data set Configuration").
Script also prepare merging for each group (done in BEH2) and checks for validity effect per participant.
DON'T FORGET TO TAG REMOVED ARTIFACT-EPOCH IN DATASET CONF
Look for "# Particpant ID" to configure participant details


# R Setup
```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(patchwork)
library(cowplot)
library(tidyverse)
```

# Data set Configuration
```{r, message=FALSE, warning=FALSE, include=F}

# Select Participant
grp <- "C"
num <- "4"
ID <- paste0("participant_", num)
participantSave <- paste0(grp, "_", num)
```


## 1) Merge Blocks
```{r, message=FALSE, warning=FALSE}

fpath <- paste0("C:/MATLAB/exp_1/results/BEH/", grp, "/", ID, '/')

if(file.exists(paste0(fpath, "block_1.csv"))) {
  block_1 <- read_csv(paste0(fpath, "block_1.csv"))
} 
if(file.exists(paste0(fpath, "block_2.csv"))) {
  block_2 <- read_csv(paste0(fpath, "block_2.csv"))
} 
if(file.exists(paste0(fpath, "block_3.csv"))) {
  block_3 <- read_csv(paste0(fpath, "block_3.csv"))
} 
if(file.exists(paste0(fpath, "block_4.csv"))) {
  block_4 <- read_csv(paste0(fpath, "block_4.csv"))
} 
if(file.exists(paste0(fpath, "block_5.csv"))) {
  block_5 <- read_csv(paste0(fpath, "block_5.csv"))
}

# Merge each participant's blocks
if (exists("block_5") && !is.null(block_5)) {
  rawData <- full_join(block_1, block_2) |>
                full_join(block_3) |>
                full_join(block_4) |>
                full_join(block_5) |>
                mutate(id = ID,
                       group = grp,
                       .before = 1)
} else {
  rawData <- full_join(block_1, block_2) |>
              full_join(block_3) |>
              full_join(block_4) |>
              mutate(id = ID,
                     group = grp,
                     .before = 1)
}
# # Alternative
# fileList <- c(paste0(fpath, "block_1.csv"),
#               paste0(fpath, "block_2.csv"),
#               paste0(fpath, "block_3.csv"),
#               paste0(fpath, "block_4.csv")
#               )
#
# rawData <- lapply(fileList, read_csv) |>
#                 bind_rows() |>
#                 mutate(id = ID,
#                        group = grp, 
#                        .before = 1)
```

## 2) Recategorise & Relabel
Make sure triggers are set as character/factor and not numbers. Also relabel for easier input
```{r, message=FALSE, warning=FALSE}
# Set all matrices from numeric to character
rawData$fixJitData <- as.character(rawData$fixJitData)
rawData$cueJitData <- as.character(rawData$cueJitData)
rawData$trialType <- as.character(rawData$trialType) # 0 = NoGrat; 1 = Grat > CHANGE TO LABEL
rawData$cuePos <- as.character(rawData$cuePos) # 0 = left; 1 = right; 2 = Neutral > CHANGE TO LABEL
rawData$targetLR <- as.character(rawData$targetLR) # 0 = left; 1 = right > CHANGE TO LABEL
rawData$gapLoc <- as.character(rawData$gapLoc) # specific gap location
rawData$validity <- as.character(rawData$validity) # 0 = invalid; 1 = valid; 2 = neutral > CHANGE TO LABEL
rawData$correctDet <- as.character(rawData$correctDet) # 0 = incorrect; 1 = correct > CHANGE TO LABEL
rawData$correctAcc <- as.character(rawData$correctAcc) # 0 = incorrect; 1 = correct > CHANGE TO LABEL

# Relabel (in case of filter, easier to id)
rawData <- 
  rawData |>
  mutate(trialType = recode(trialType, "0" = "NG", 
                                       "1" = "G"),
         
         cuePos = recode(cuePos, "0" = "left", 
                                 "1" = "right", 
                                 "2" ="neutral"),
         
         targetLR = recode(targetLR, "0" = "left", 
                                     "1" = "right"),
         
         validity = recode(validity, "0" = "invalid", 
                                     "1" = "valid", 
                                     "2" = "neutral"),
         
         correctDet = recode(correctDet, "0" = "incorrect", 
                                         "1" = "correct"),
         
         correctAcc = recode(correctAcc, "0" = "incorrect", 
                                         "1" = "correct")
         )
```

## 3) Give Trial Number

This code chunk separates the raw data set by each trialType (i.e. NG L-R-N & G L-R-N) 
and gives number for each condition group (i.e. #1:end for every trialType) to match with EEG epochs numbers

```{r, message=FALSE, warning=FALSE}

# Fieldtrip only number each epoch, does not seperate them
# rawData <-
#   rawData |> 
#   mutate(numLabel = as.character(1:n()),
#          .before = 1)

rawData <-
  rawData |> 
  mutate(numLabel = 1:n(),
         .before = 1)
```

## 4) Initial Cut-off & Outlier Removal
```{r, message=FALSE, warning=FALSE}

# Set Initial rtDet cut-off
mean_rt <- mean(rawData$rtDet)
sd_rt <- sd(rawData$rtDet)

# RT below 02. secs
cutoffOut1 <-
  rawData |>
  filter(rtDet < 0.2) 
cutoffOut1 <- cutoffOut1$numLabel
# RT above 2.5 sd
cutoffOut2 <-
  rawData |>
  filter(rtDet > mean_rt + 2.5*sd_rt) 
cutoffOut2 <- cutoffOut2$numLabel

cutoffOut <- c(cutoffOut1, cutoffOut2)

rawData <-
  rawData |> 
  filter(!numLabel %in% cutoffOut)

# <<<<<<<<<<< OUTLIER METHOD >>>>>>>>>>>  

# Z Score
DataZ <- rawData |>
  mutate(zscore = (rtDet - mean(rtDet))/sd(rtDet)) |>
  filter(zscore > -3 & zscore < 3)

# <<<<<<<<<<<<<<<< OR >>>>>>>>>>>>>>>>>>>

# 2sd
mean_rt <- mean(rawData$rtDet)
sd_rt <- sd(rawData$rtDet)
Data2sd <- rawData |>
  filter(rtDet > mean_rt - 2.5*sd_rt & rtDet < mean_rt + 2.5*sd_rt)

# <<<<<<<<<<<<<<<< OR >>>>>>>>>>>>>>>>>>>

# IQR
DataIQR <- 
  rawData|>
  rstatix::identify_outliers(rtDet)
# List every rtDet classified as outlier (is.outlier vs is.extreme)
outlierList <- c(DataIQR$rtDet[DataIQR$is.outlier == TRUE])
# Remove rows with outlier based on above (DataIQR for visualisation purposes)
DataIQR <- 
  rawData|>
  filter(!rtDet %in% outlierList[])

```

## 5) Compare distribution (before/after)
```{r, message=FALSE, warning=FALSE}
# before removal
distCheck <- 
  ggplot(rawData, aes(rtDet)) +
  geom_histogram(bins = 50) + 
  labs(title = "Before Outlier Removal")
print(distCheck)

# IQR removal
distCheckIQR <- 
  ggplot(DataIQR, aes(rtDet)) + 
  geom_histogram(bins = 50) + 
  labs(title = "IQR")
print(distCheckIQR)

#Z removal
distCheckZ <- ggplot(DataZ, aes(rtDet)) + geom_histogram(bins = 50) + labs(title = "Z Score")
print(distCheckZ)

#2SD removal
distCheck2sd <- ggplot(Data2sd, aes(rtDet)) + geom_histogram(bins = 50) + labs(title = "2SD")
print(distCheck2sd)
```

## 6) Summary Descriptive
```{r, message=FALSE, warning=FALSE}
# rawData|>
#   group_by(validity, targetLR, trialType) |>
#   get_summary_stats(rtDet, type = "mean_sd") |>
# 
#   flextable(cwidth = .95) |>
#   fontsize(size = 8) |>
#   fontsize(size = 10, part = "header") |>
# 
#   set_header_labels(validity = "Validity",
#                     targetLR = "Left/Right Target",
#                     trialType = "Gratings",
#                     variable = "Variable")
```

# Match data with EEG data

In order to have clean correct EEG data (correct answers) we need to remove the epoch/trial number in the EEG data 
where it is incorrect behaviourally. Chunk below retrieve the number of the incorrect trials/epochs the retrieved numbers will then be fee to the EEG script, isolating the beh-correct EEG trials only.

## 7) Identify the numLabel for removed BEH outlier (just tagging) - format: #epoch based on reaction time tagging
Seperated to know how much were excluded per condition. Note: this was build for EEGLAB compatibility, not necessary in fieldtrip (i.e. in how both epoch data)

```{r}
# NG Left
behOut <- 
  rawData|>
  filter(rtDet %in% outlierList[], # filter/find rows where rtDet is in the outlierList
         trialType == "NG",
         cuePos == "left")
behOut_NG_L <- behOut$numLabel

# NG Right
behOut <- 
  rawData|>
  filter(rtDet %in% outlierList[],
         trialType == "NG",
         cuePos == "right")
behOut_NG_R <- behOut$numLabel

# NG Neutral
behOut <- 
  rawData|>
  filter(rtDet %in% outlierList[],
         trialType == "NG",
         cuePos == "neutral")
behOut_NG_N <- behOut$numLabel

# G Left
behOut <- 
  rawData|>
  filter(rtDet %in% outlierList[],
         trialType == "G",
         cuePos == "left")
behOut_G_L <- behOut$numLabel

# G Right
behOut <- 
  rawData|>
  filter(rtDet %in% outlierList[],
         trialType == "G",
         cuePos == "right")
behOut_G_R <- behOut$numLabel

# G Neutral
behOut <- 
  rawData|>
  filter(rtDet %in% outlierList[],
         trialType == "G",
         cuePos == "neutral")
behOut_G_N <- behOut$numLabel

```

## 8) Identify the numLabel for removed EEG outlier (i.e. bad eeg epochs) - format: #epoch tagging
```{r, message=FALSE, warning=FALSE}

# bad epochs in eeg data
eegOut<- c()
eegOut <- as.integer(eegOut)

```

## 9) Filter out tagged numLabel (EEG & BEH) from data set per trialType-cuePos
```{r}
## NG Left
clean_NG_L <- 
  rawData |>
  filter(trialType == "NG",
         cuePos == "left",
         !numLabel %in% behOut_NG_L[],
         !numLabel %in% eegOut[])

## NG Right
clean_NG_R <- 
  rawData |>
  filter(trialType == "NG",
         cuePos == "right",
         !numLabel %in% behOut_NG_R[],
         !numLabel %in% eegOut[])

## NG Neutral
clean_NG_N <- 
  rawData |>
  filter(trialType == "NG",
         cuePos == "neutral",
         !numLabel %in% behOut_NG_N[],
         !numLabel %in% eegOut[])

## G Left
clean_G_L <- 
  rawData |>
  filter(trialType == "G",
         cuePos == "left",
         !numLabel %in% behOut_G_L[],
         !numLabel %in% eegOut[])

## G Right
clean_G_R <- 
  rawData |>
  filter(trialType == "G",
         cuePos == "right",
         !numLabel %in% behOut_G_R[],
         !numLabel %in% eegOut[])

## G Neutral
clean_G_N <- 
  rawData |>
  filter(trialType == "G",
         cuePos == "neutral",
         !numLabel %in% behOut_G_N[],
         !numLabel %in% eegOut[])
```

## 10) Remerge, filter cut-off, and  save clean (from EEG artifact and BEH outlier) data set
```{r}
## Remerge clean data set
cleanData <- 
  full_join(clean_NG_L, clean_NG_R) |>
  full_join(clean_NG_N) |>
  full_join(clean_G_L) |>
  full_join(clean_G_R) |>
  full_join(clean_G_N) 
# |> 
#   filter(between(rtDet, 0.2, 5))

write_csv(cleanData, paste0("C:/R/exp_1/results/BEH/indv_merge_dataset/", participantSave, ".csv"))
```
## Combine removed numLabel & Export to Matlab
```{r}

cutoffOut <- data.frame(numLabel = cutoffOut)
behOut <- data.frame(numLabel = c(behOut_NG_L, behOut_NG_R, behOut_NG_N, 
                                  behOut_G_L, behOut_G_R, behOut_G_N))
eegOut <- data.frame(numLabel = eegOut)

beh_out <-
  full_join(cutoffOut, behOut) |> 
  full_join(eegOut)
beh_out <- sort(beh_out$numLabel, decreasing=F)
beh_out <- as.numeric(beh_out)

# # tidyverse
# beh_out <-
#   full_join(cutoffOut, behOut) |> 
#   full_join(eegOut) |> 
#   arrange(numLabel)
# beh_out
# beh_out <- as.numeric(beh_out)

# fpMat = paste0("C:\MATLAB\exp_1\results\EEG\", grp,  )
fpMat <- paste0("C:/MATLAB/exp_1/results/EEG/", grp, "/participant_", num, "/")
R.matlab::writeMat(paste0(fpMat, "beh_out.mat"), beh_out = beh_out)
```

# Obtain percentage on accurate response
only for correct detection and accurate response
```{r, message=F, warning=F}
# Full data
# full data for denominator
denom <- 
  cleanData |> 
  filter(correctDet == "correct") # >>>>>>>>>>>>>> all correct detection

acc <-
  denom |> 
  filter(correctAcc == "correct") # >>>>>>>>>>>>>> all accurate response

all_all_num_out <- nrow(cleanData) - nrow(acc) # how many excluded if only want accurate reponses
all_all <- nrow(acc)/nrow(denom) # accurate response / correct detection (change to % below)

# Valid
denom <- 
  cleanData |> 
  filter(validity == "valid",
         correctDet == "correct")

acc <-
  denom |> 
  filter(correctAcc == "correct")

all_valid_num_out <- nrow(filter(cleanData, validity == "valid")) - nrow(acc)
all_valid <- nrow(acc)/nrow(denom)

# Invalid
denom <- 
  cleanData |> 
  filter(validity == "invalid",
         correctDet == "correct")

acc <-
  denom |> 
  filter(correctAcc == "correct")

all_invalid_num_out <- nrow(filter(cleanData, validity == "invalid")) - nrow(acc)
all_invalid <- nrow(acc)/nrow(denom)

# Neutral
denom <- 
  cleanData |> 
  filter(validity == "neutral",
         correctDet == "correct")

acc <-
  denom |> 
  filter(correctAcc == "correct")

all_neutral_num_out <- nrow(filter(cleanData, validity == "neutral")) - nrow(acc)
all_neutral <- nrow(acc)/nrow(denom)

# >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
# NG
# All
denom <- 
  cleanData |> 
  filter(trialType == "NG",
         correctDet == "correct")

acc <-
  denom |> 
  filter(correctAcc == "correct")

NG_all_num_out <- nrow(filter(cleanData, trialType == "NG")) - nrow(acc)
NG_all <- nrow(acc)/nrow(denom)

# Valid
denom <- 
  cleanData |> 
  filter(trialType == "NG",
         validity == "valid",
         correctDet == "correct")

acc <-
  denom |> 
  filter(correctAcc == "correct")

NG_valid_num_out <- nrow(filter(cleanData, trialType == "NG", validity == "valid")) - nrow(acc)
NG_valid <- nrow(acc)/nrow(denom)

# Invalid
denom <- 
  cleanData |> 
  filter(trialType == "NG",
         validity == "invalid",
         correctDet == "correct")

acc <-
  denom |> 
  filter(correctAcc == "correct")

NG_invalid_num_out <- nrow(filter(cleanData, trialType == "NG", validity == "invalid")) - nrow(acc)
NG_invalid <- nrow(acc)/nrow(denom)

# Neutral
denom <- 
  cleanData |> 
  filter(trialType == "NG",
         validity == "neutral",
         correctDet == "correct")

acc <-
  denom |> 
  filter(correctAcc == "correct")

NG_neutral_num_out <- nrow(filter(cleanData, trialType == "NG", validity == "neutral")) - nrow(acc)
NG_neutral <- nrow(acc)/nrow(denom)
# >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
# G
# All
denom <- 
  cleanData |> 
  filter(trialType == "G",
         correctDet == "correct")

acc <-
  denom |> 
  filter(correctAcc == "correct")

G_all_num_out <- nrow(filter(cleanData, trialType == "G")) - nrow(acc)
G_all <- nrow(acc)/nrow(denom)

# G Valid
denom <- 
  cleanData |> 
  filter(trialType == "G",
         validity == "valid",
         correctDet == "correct")

acc <-
  denom |> 
  filter(correctAcc == "correct")

G_valid_num_out <- nrow(filter(cleanData, trialType == "G", validity == "valid")) - nrow(acc)
G_valid <- nrow(acc)/nrow(denom)

# G Invalid
denom <- 
  cleanData |> 
  filter(trialType == "G",
         validity == "invalid",
         correctDet == "correct")

acc <-
  denom |> 
  filter(correctAcc == "correct")

G_invalid_num_out <- nrow(filter(cleanData, trialType == "G", validity == "invalid")) - nrow(acc)
G_invalid <- nrow(acc)/nrow(denom)

# G Neutral
denom <- 
  cleanData |> 
  filter(trialType == "G",
         validity == "neutral",
         correctDet == "correct")

acc <-
  denom |> 
  filter(correctAcc == "correct")

G_neutral_num_out <- nrow(filter(cleanData, trialType == "G", validity == "neutral")) - nrow(acc)
G_neutral <- nrow(acc)/nrow(denom)

# >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
# Create new data set for percentage
percAcc <- 
  data.frame(group = grp,
             id = ID,
             all_all = all_all*100,
             all_valid = all_valid*100,
             all_invalid = all_invalid*100,
             all_neutral = all_neutral*100,
             NG_all = NG_all*100,
             NG_valid = NG_valid*100,
             NG_invalid = NG_invalid*100,
             NG_neutral = NG_neutral*100,
             G_all = G_all*100,
             G_valid = G_valid*100,
             G_invalid = G_invalid*100,
             G_neutral = G_neutral*100
             )

# Final accuracy data
write_csv(percAcc, paste0("C:/R/exp_1/results/BEH/indv_merge_dataset_acc/", participantSave, ".csv"))

# Create new data set for percentage
num_out <- 
  data.frame(group = grp,
             id = ID,
             all_all = (all_all_num_out/nrow(cleanData))*100, 
             all_valid = (all_valid_num_out/nrow(filter(cleanData, validity == "valid")))*100,
             all_invalid = (all_invalid_num_out/nrow(filter(cleanData, validity == "invalid")))*100,
             all_neutral = (all_neutral_num_out/nrow(filter(cleanData, validity == "neutral")))*100,
             NG_all = (NG_all_num_out/nrow(filter(cleanData, trialType == "NG")))*100,
             NG_valid = (NG_valid_num_out/nrow(filter(cleanData, trialType == "NG", validity == "valid")))*100,
             NG_invalid = (NG_invalid_num_out/nrow(filter(cleanData, trialType == "NG", validity == "invalid")))*100,
             NG_neutral = (NG_neutral_num_out/nrow(filter(cleanData, trialType == "NG", validity == "neutral")))*100,
             G_all = (G_all_num_out/nrow(filter(cleanData, trialType == "G")))*100,
             G_valid = (G_valid_num_out/nrow(filter(cleanData, trialType == "G", validity == "valid")))*100,
             G_invalid = (G_invalid_num_out/nrow(filter(cleanData, trialType == "G", validity == "invalid")))*100,
             G_neutral = (G_neutral_num_out/nrow(filter(cleanData, trialType == "G", validity == "neutral")))*100
             ) |> 
  pivot_longer(cols = 3:14,
               names_to = c("trialType", "validity"),
               names_sep = "_",
               values_to = "percentage") |> 
  mutate(percentage = round(percentage, 2))

write_csv(num_out, paste0("C:/R/exp_1/results/BEH/indv_merge_dataset_num_out/", participantSave, ".csv"))
  
num_out
```

## 11) Compare data set (Precaution)
just in case manual tagging in 8-10 might be wrong, always recheck against the auto IQR removal data set
```{r, message=FALSE, warning=FALSE}
# Behaviour outlier removal in the cleanData is based on comparing rtDet in 6 decimal places.
# Do this to make sure cleanData match DataIQR
arsenal::comparedf(cleanData, DataIQR)
```

## 12) Validity Reaction Time Plot - Correct Responses Only
Check for validity effect, mark participants with no effect
```{r, message=FALSE, warning=FALSE}

data <- cleanData

# NoGrat
noGratRt <- 
  filter(data,
         trialType == "NG",  # Only want NoGrat
         correctDet == "correct") # Only want correct response
# Set plot contents
noGratRt <- 
 ggplot(noGratRt, aes(validity, rtDet, fill = validity)) + 
  # Set whiskers
  stat_boxplot(geom = 'errorbar', 
               width = 0.3, 
               coef = 1.5) +
  # Set plot design
  geom_jitter(aes(color=validity), 
              width = 0.3, 
              alpha = 0.1) +
  scale_color_manual(values=c("indianred3", "limegreen", "dodgerblue"))  +
  guides(color = FALSE) +
  geom_boxplot(alpha = 0.8, 
               outlier.shape = NaN) +
  # Set mean
  stat_summary(fun = mean, 
               geom = "point", 
               shape = 18, 
               size = 3, 
               show.legend = F) +
  # Set major labels (title, Y, X axis)
  labs(title = "No Gratings",
       x = " ",
       y = "RT (Secs)") +
  # Rename each X axis character label
  scale_x_discrete(limits = c("invalid", "valid", "neutral"),
                   labels = c("Invalid", "Valid", "Neutral")) +
  # Set Y axis range
  ylim(0, 3) +
  # Set colour
  scale_fill_manual(values=c("coral", "seagreen1", "cadetblue1")) +
  # Plot theme
  theme_bw() +
  # Remove legend
  guides(fill=FALSE)


# Gratings
gratRt <- filter(data,
                 trialType == "G",
                 correctDet == "correct")
# Set plot contents
gratRt <- 
  ggplot(gratRt, aes(validity, rtDet, fill = validity)) + 
  # Set whiskers
  stat_boxplot(geom = 'errorbar', 
               width = 0.3, 
               coef = 1.5) +
  # Set plot design
  geom_jitter(aes(color=validity), 
              width = 0.3, 
              alpha = 0.1) +
  scale_color_manual(values=c("indianred3", "limegreen", "dodgerblue"))  +
  guides(color = FALSE) +
  geom_boxplot(alpha = 0.8, 
               outlier.shape = NaN) +
  # Set mean
  stat_summary(fun = mean, 
               geom = "point", 
               shape = 18, 
               size = 3, 
               show.legend = F) +
  # Set major labels (title, Y, X axis)
  labs(title = "No Gratings",
       x = " ",
       y = "RT (Secs)") +
  # Rename each X axis character label
  scale_x_discrete(limits = c("invalid", "valid", "neutral"),
                   labels = c("Invalid", "Valid", "Neutral")) +
  # Set Y axis range
  ylim(0, 3) +
  # Set colour
  scale_fill_manual(values=c("coral", "seagreen1", "cadetblue1")) +
  # Plot theme
  theme_bw() +
  # Remove legend
  guides(fill=FALSE)

rtPlot <- noGratRt + gratRt
# ggsave("C:/MATLAB/exp_1/results/figures/RT_plot.png", rtPlot)
print(rtPlot)
# rtPlot <- plot_grid(noGratRt, gratRt, labels=c("A", "B"), ncol = 2, nrow = 1)
# # ggsave("C:/MATLAB/exp_1/results/figures/RT_plot.png", rtPlot)
# print(rtPlot)
```

-------------------------------------------------------------------------------------------------------------------------

-------------------------------------------[CTRL + SHIFT + ALT + P] FROM HERE--------------------------------------------

-------------------------------------------------------------------------------------------------------------------------

# Particpant ID
Configure which participant to preprocess here. Then ctrl+shift+alt+p from above.
```{r, message=FALSE, warning=FALSE}
# Clear environment
rm(list = ls())
# Select Participant
grp <- "C"
num <- "4"
ID <- paste0("participant_", num)
participantSave <- paste0(grp, "_", num)
```
--------------------------------------------------------------------------------------------------------------------------

## Summary Descriptive
```{r, message=FALSE, warning=FALSE}
# rawData|>
#   group_by(validity, targetLR, trialType) |>
#   get_summary_stats(rtDet, type = "mean_sd") |>
# 
#   flextable(cwidth = .95) |>
#   fontsize(size = 8) |>
#   fontsize(size = 10, part = "header") |>
# 
#   set_header_labels(validity = "Validity",
#                     targetLR = "Left/Right Target",
#                     trialType = "Gratings",
#                     variable = "Variable")
```



























































# NOT DONE
# New Percentage Data frame
```{r}

# # Full raw data set for each validity type
# rawData_Val <- rawData |> filter(validity == "valid")
# rawData_Inval <-  rawData |> filter(validity == "invalid")
# rawData_Neut <-  rawData |> filter(validity == "neutral")
# 
# # Correct only data set per validity type
# alphaBeh_Val <- alphaBeh |> filter(validity == "valid")
# alphaBeh_Inval <-  alphaBeh |> filter(validity == "invalid")
# alphaBeh_Neut <-  alphaBeh |> filter(validity == "neutral")
# 
# # NG raw data set for each validity type
# rawDataNG <- rawData |> filter(trialType == "NG")
# rawDataNG_Val <- rawDataNG |> filter(validity == "valid")
# rawDataNG_Inval <- rawDataNG |> filter(validity == "invalid")
# rawDataNG_Neut <- rawDataNG |> filter(validity == "neutral")
# 
# # G raw data set for each validity type
# rawDataG <- rawData |> filter(trialType == "G")
# rawDataG_Val <- rawDataG |> filter(validity == "valid")
# rawDataG_Inval <- rawDataG |> filter(validity == "invalid")
# rawDataG_Neut <- rawDataG |> filter(validity == "neutral")
# 
# # Correct only NG data set per validity type
# alphaBehNG <- alphaBeh |> filter(trialType == "NG")
# alphaBehNG_Val <- alphaBehNG |> filter(validity == "valid")
# alphaBehNG_Inval <- alphaBehNG |> filter(validity == "invalid")
# alphaBehNG_Neut <- alphaBehNG |> filter(validity == "neutral")
# 
# # Correct only G data set per validity type
# alphaBehG <- alphaBeh |> filter(trialType == "G")
# alphaBehG_Val <- alphaBehG |> filter(validity == "valid")
# alphaBehG_Inval <- alphaBehG |> filter(validity == "invalid")
# alphaBehG_Neut <- alphaBehG |> filter(validity == "neutral")
# 
# percAcc <- data.frame(group = grp,
#                       id = ID,
#                       tTcollapsed = (nrow(alphaBeh) / nrow(rawData)),
#                       tTcollapsed_Val = (nrow(alphaBeh_Val) / nrow(rawData_Val)),
#                       tTcollapsed_Inval = (nrow(alphaBeh_Inval) / nrow(rawData_Inval)),
#                       tTcollapsed_Neut = (nrow(alphaBeh_Neut) / nrow(rawData_Neut)),
#                       allNG = (nrow(alphaBehNG) / nrow(rawDataNG)),
#                       NG_Val = (nrow(alphaBehNG_Val) / nrow(rawDataNG_Val)),
#                       NG_Inval = (nrow(alphaBehNG_Inval) / nrow(rawDataNG_Inval)),
#                       NG_Neut = (nrow(alphaBehNG_Neut) / nrow(rawDataNG_Neut)),
#                       allG = (nrow(alphaBehG) / nrow(rawDataG)),
#                       G_Val = (nrow(alphaBehG_Val) / nrow(rawDataG_Val)),
#                       G_Inval = (nrow(alphaBehG_Inval) / nrow(rawDataG_Inval)),
#                       G_Neut =(nrow(alphaBehG_Neut) / nrow(rawDataG_Neut))
#                       )
# # 
# # write_csv(percAcc, paste0("C:/R/exp_1/results/BEH/indv_merge_dataset/alphaBeh/", participantSave, ".csv"))
```

# To view removed BEH label
```{r}
# # Easier to view removed label (trial) for each Det and Acc to match EEG Data
# maxLength <- max(c(length(beh_NG_L_Det), length(beh_NG_L_Acc), 
#                  length(beh_NG_R_Det), length(beh_NG_R_Acc), 
#                  length(beh_NG_N_Det), length(beh_NG_N_Acc), 
#                  length(beh_G_L_Det), length(beh_G_L_Acc), 
#                  length(beh_G_R_Det), length(beh_G_R_Acc), 
#                  length(beh_G_N_Det), length(beh_G_N_Acc))) 
# 
# eeg_beh_list <- data.frame(NG_L_Det = c(beh_NG_L_Det,rep(NA, maxLength - length(beh_NG_L_Det))),
#                            NG_L_Acc = c(beh_NG_L_Acc,rep(NA, maxLength - length(beh_NG_L_Acc))),
#                            NG_R_Det = c(beh_NG_R_Det,rep(NA, maxLength - length(beh_NG_R_Det))),
#                            NG_R_Acc = c(beh_NG_R_Acc,rep(NA, maxLength - length(beh_NG_R_Acc))),
#                            NG_N_Det = c(beh_NG_N_Det,rep(NA, maxLength - length(beh_NG_N_Det))),
#                            NG_N_Acc = c(beh_NG_N_Acc,rep(NA, maxLength - length(beh_NG_N_Acc))),
#                            G_L_Det = c(beh_G_L_Det,rep(NA, maxLength - length(beh_G_L_Det))),
#                            G_L_Acc = c(beh_G_L_Acc,rep(NA, maxLength - length(beh_G_L_Acc))),
#                            G_R_Det = c(beh_G_R_Det,rep(NA, maxLength - length(beh_G_R_Det))),
#                            G_R_Acc = c(beh_G_R_Acc,rep(NA, maxLength - length(beh_G_R_Acc))),
#                            G_N_Det = c(beh_G_N_Det,rep(NA, maxLength - length(beh_G_N_Det))),
#                            G_N_Acc = c(beh_G_N_Acc,rep(NA, maxLength - length(beh_G_N_Acc))))
```


>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>

## This code chunk seperates the raw data set by each trialType (i.e. NG LRN & G LRN) 
# and gives number for each conditions (i.e. 1:end for every trialType) to match with EEG epochs

```{r, message=FALSE, warning=FALSE}

# ## NG Left
# 
# alphaBeh_NG_L <- rawData |>
#                     filter(trialType == "NG",
#                            cuePos == "left") |>
# # numLabel each trialType with numbers (i.e. new column with numbers starting from 1:last row)
#                     mutate(numLabel = as.character(1:n()),
#                            .before = 1)
# 
# ## NG Right
# 
# alphaBeh_NG_R <- rawData |>
#                     filter(trialType == "NG",
#                            cuePos == "right") |>
# # numLabel each trialType with numbers (i.e. new column with numbers starting from 1:last row)
#                     mutate(numLabel = as.character(1:n()),
#                            .before = 1)
# 
# ## NG Neutral
# 
# alphaBeh_NG_N <- rawData |>
#                     filter(trialType == "NG",
#                            cuePos == "neutral") |>
# # numLabel each trialType with numbers (i.e. new column with numbers starting from 1:last row)
#                     mutate(numLabel = as.character(1:n()),
#                            .before = 1)
# 
# ## G Left
# 
# alphaBeh_G_L <- rawData |>
#                     filter(trialType == "G",
#                            cuePos == "left") |>
# # numLabel each trialType with numbers (i.e. new column with numbers starting from 1:last row)
#                     mutate(numLabel = as.character(1:n()),
#                            .before = 1)
# 
# ## G Right
# 
# alphaBeh_G_R <- rawData |>
#                     filter(trialType == "G",
#                            cuePos == "right") |>
# # numLabel each trialType with numbers (i.e. new column with numbers starting from 1:last row)
#                     mutate(numLabel = as.character(1:n()),
#                            .before = 1)
# 
# ## G Neutral
# 
# alphaBeh_G_N <- rawData |>
#                     filter(trialType == "G",
#                            cuePos == "neutral") |>
# # numLabel each trialType with numbers (i.e. new column with numbers starting from 1:last row)
#                     mutate(numLabel = as.character(1:n()),
#                            .before = 1)
# 
# ## Remerge seperated data set
# 
# rawData <- full_join(alphaBeh_NG_L, alphaBeh_NG_R) |>
#               full_join(alphaBeh_NG_N)|>
#               full_join(alphaBeh_G_L)|>
#               full_join(alphaBeh_G_R)|>
#               full_join(alphaBeh_G_N)

```









