---
title: "BEH2_merge"
author: "Leonardo Sutandi"
date: "2025-03-13"
output: html_document
---

## R Setup
```{r setup, include=T}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# A) Reaction Time
This script merge preprocessed individual data set. Outputs are: mergedC (all controls), mergedMA (all MA), 
mergedMO (all MO), and allGroups (all groups combine). Outputs with _OL are per group outlier removed output.
```{r}

# >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
# Reaction Time >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
# >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
#
# # Clear environment
# rm(list = ls())
# # loading filepath
# filepath_in <- "C:/R/exp_1/results/BEH/indv_merge_dataset/"
# # Saving filepath
# filepath_out <- "C:/R/exp_1/results/BEH/merged_group_dataset/"

# >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
# Accuracy >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
# >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
#
# Clear environment
rm(list = ls())
# loading filepath
filepath_in <- "C:/R/exp_1/results/BEH/indv_merge_dataset_acc/"
# Saving filepath
filepath_out <- "C:/R/exp_1/results/BEH/merged_group_dataset_acc/"
```


## 1) C Read Dataset
```{r, message=FALSE, warning=FALSE}

# Read all C participants
C_4 <- read_csv(paste0(filepath_in, "C_4.csv"))
C_5 <- read_csv(paste0(filepath_in, "C_5.csv"))
C_6 <- read_csv(paste0(filepath_in, "C_6.csv"))
C_8 <- read_csv(paste0(filepath_in, "C_8.csv"))
C_12 <- read_csv(paste0(filepath_in, "C_12.csv"))
C_13 <- read_csv(paste0(filepath_in, "C_13.csv"))
C_14 <- read_csv(paste0(filepath_in, "C_14.csv"))
C_15 <- read_csv(paste0(filepath_in, "C_15.csv"))
# C_16 <- read_csv(paste0(filepath_in, "C_16.csv"))
# C_18 <- read_csv(paste0(filepath_in, "C_18.csv"))
C_19 <- read_csv(paste0(filepath_in, "C_19.csv"))
C_22 <- read_csv(paste0(filepath_in, "C_22.csv"))
C_25 <- read_csv(paste0(filepath_in, "C_25.csv"))
# C_26 <- read_csv(paste0(filepath_in, "C_26.csv"))
# C_28 <- read_csv(paste0(filepath_in, "C_28.csv"))
C_29 <- read_csv(paste0(filepath_in, "C_29.csv"))
C_31 <- read_csv(paste0(filepath_in, "C_31.csv"))
C_36 <- read_csv(paste0(filepath_in, "C_36.csv"))
C_37 <- read_csv(paste0(filepath_in, "C_37.csv")) #15 stops here
C_38 <- read_csv(paste0(filepath_in, "C_38.csv"))
C_40 <- read_csv(paste0(filepath_in, "C_40.csv"))
# C_41 <- read_csv(paste0(filepath_in, "C_41.csv")) 

# Merge all controls
mergedC <- 
  full_join(C_4, C_5) |>
  full_join(C_6) |>
  full_join(C_8) |>
  full_join(C_12) |>
  full_join(C_13) |>
  full_join(C_14) |>
  full_join(C_15) |>
  # full_join(C_16) |>
  # full_join(C_18) |>
  full_join(C_19) |>
  full_join(C_22) |>
  full_join(C_25) |>
  # full_join(C_26) |>
  # full_join(C_28) |>
  full_join(C_29) |>
  full_join(C_31) |>
  full_join(C_36) |> 
  full_join(C_37) |> 
  full_join(C_38) |> 
  full_join(C_40)

# Save C merged dataset
write_csv(mergedC, paste0(filepath_out, "mergedC.csv"))
```

# 2) Control Outlier Removal
```{r}
# # IQR
# mergedC_OL <- mergedC|>
#   rstatix::identify_outliers(rtDet)
# # List every rtDet classified as outlier (is.outlier vs is.extreme)
# outlierListC <- c(mergedC_OL$rtDet[mergedC_OL$is.outlier == TRUE])
# # Remove rows with outlier based on above
# mergedC_OL <- mergedC|>
#   filter(!rtDet %in% outlierListC[])
# 
# write_csv(mergedC_OL, paste0(filepath_out, "mergedC_OL.csv"))
```

## 3) MA Read Dataset
```{r, message=FALSE, warning=FALSE}
# Read all MA participants
MA_7 <- read_csv(paste0(filepath_in, "MA_7.csv"))
MA_9 <- read_csv(paste0(filepath_in, "MA_9.csv"))
MA_11 <- read_csv(paste0(filepath_in, "MA_11.csv"))
MA_20 <- read_csv(paste0(filepath_in, "MA_20.csv"))
MA_21 <- read_csv(paste0(filepath_in, "MA_21.csv"))
MA_24 <- read_csv(paste0(filepath_in, "MA_24.csv"))
MA_27 <- read_csv(paste0(filepath_in, "MA_27.csv"))
MA_30 <- read_csv(paste0(filepath_in, "MA_30.csv"))
MA_33 <- read_csv(paste0(filepath_in, "MA_33.csv"))
MA_34 <- read_csv(paste0(filepath_in, "MA_34.csv"))
MA_35 <- read_csv(paste0(filepath_in, "MA_35.csv"))
MA_39 <- read_csv(paste0(filepath_in, "MA_39.csv"))

# Merge to 1 dataset
mergedMA <- 
  full_join(MA_7, MA_9) |>
  full_join(MA_11) |>
  full_join(MA_20) |>
  full_join(MA_21) |>
  full_join(MA_24) |>
  full_join(MA_27) |>
  full_join(MA_30) |>
  full_join(MA_33) |>
  full_join(MA_34) |>
  full_join(MA_35) |> 
  full_join(MA_39)

# Save MA merged dataset
write_csv(mergedMA, paste0(filepath_out, "mergedMA.csv"))
```

# 4) MA Outlier Removal
```{r}
# # IQR
# mergedMA_OL <- mergedMA|>
#   rstatix::identify_outliers(rtDet)
# # List every rtDet classified as outlier (is.outlier vs is.extreme)
# outlierListMA <- c(mergedMA_OL$rtDet[mergedMA_OL$is.outlier == TRUE])
# # Remove rows with outlier based on above
# mergedMA_OL <- mergedMA|>
#   filter(!rtDet %in% outlierListMA[])
# 
# write_csv(mergedMA_OL, paste0(filepath_out, "mergedMA_OL.csv"))
```

# 5) MO Read Data Set
```{r, message=FALSE, warning=FALSE}
# Read all MO participants
MO_2 <- read_csv(paste0(filepath_in, "MO_2.csv"))
MO_3 <- read_csv(paste0(filepath_in, "MO_3.csv"))
MO_10 <- read_csv(paste0(filepath_in, "MO_10.csv"))
MO_17 <- read_csv(paste0(filepath_in, "MO_17.csv"))
MO_32 <- read_csv(paste0(filepath_in, "MO_32.csv"))

# Merge to 1 dataset
mergedMO <- full_join(MO_2, MO_3) |> 
            full_join(MO_10) |>
            full_join(MO_17) |>
            full_join(MO_32)

# Save MA merged dataset
write_csv(mergedMO, paste0(filepath_out, "mergedMO.csv"))
```

# 6) MO Outlier Removal
```{r}
# # IQR
# mergedMO_OL <- mergedMO|>
#   rstatix::identify_outliers(rtDet)
# # List every rtDet classified as outlier (is.outlier vs is.extreme)
# outlierListMO <- c(mergedMO_OL$rtDet[mergedMO_OL$is.outlier == TRUE])
# # Remove rows with outlier based on above
# mergedMO_OL <- mergedMO|>
#   filter(!rtDet %in% outlierListMO[])
# 
# write_csv(mergedMO_OL, paste0(filepath_out, "mergedMO_OL.csv"))
```

# 7) Merge Migraines (Optional)
```{r, message=FALSE, warning=FALSE}

mergedM <- full_join(mergedMO, mergedMA) |> 
  mutate(group = recode(group, "MO" = "M",
                               "MA" = "M"))

write.csv(mergedM, paste0(filepath_out, "mergedM.csv"))
```

# 8a) Combine all datasets
```{r, message=FALSE, warning=FALSE}

allGroups <- full_join(mergedC, mergedM)

write.csv(allGroups, paste0(filepath_out, "allGroups.csv"))
```

# 8b) ONLY ACCURACY DATA
```{r}
if (filepath_in == "C:/R/exp_1/results/BEH/indv_merge_dataset_acc/") {
allGroups <-
  allGroups |>
  pivot_longer(cols = 3:14,
               names_to = c("trialType", "validity"),
               names_sep = "_",
               values_to = "percentage")

write.csv(allGroups, paste0(filepath_out, "allGroups.csv"))
}
```

# 9) Combine all OL datasets
```{r, message=FALSE, warning=FALSE}
# mergedM_OL <- full_join(mergedMO_OL, mergedMA_OL) |> 
#   mutate(group = recode(group, "MO" = "M",
#                                "MA" = "M"))
# write.csv(mergedM_OL, paste0(filepath_out, "mergedM_OL.csv"))
# 
# allGroups_OL <- full_join(mergedC_OL, mergedM_OL)
# write.csv(allGroups_OL, paste0(filepath_out, "allGroups_OL.csv"))
```



























_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________

# B) Accuracy
This script merge preprocessed individual data set. Outputs are: mergedC (all controls), mergedMA (all MA), 
mergedMO (all MO), and allGroups (all groups combine). Outputs with _OL are per group outlier removed output.
```{r}
# Clear environment
rm(list = ls())
# loading filepath
filepath_in <- "C:/R/exp_1/results/BEH/indv_merge_dataset_acc/"
# Saving filepath
filepath_out <- "C:/R/exp_1/results/BEH/merged_group_dataset_acc/"
```


## 1) C Read Dataset
```{r, message=FALSE, warning=FALSE}

# Read all C participants
C_4 <- read_csv(paste0(filepath_in, "C_4.csv"))
C_5 <- read_csv(paste0(filepath_in, "C_5.csv"))
C_6 <- read_csv(paste0(filepath_in, "C_6.csv"))
C_8 <- read_csv(paste0(filepath_in, "C_8.csv"))
C_12 <- read_csv(paste0(filepath_in, "C_12.csv"))
C_13 <- read_csv(paste0(filepath_in, "C_13.csv"))
C_14 <- read_csv(paste0(filepath_in, "C_14.csv"))
C_15 <- read_csv(paste0(filepath_in, "C_15.csv"))
# C_16 <- read_csv(paste0(filepath_in, "C_16.csv"))
# C_18 <- read_csv(paste0(filepath_in, "C_18.csv"))
C_19 <- read_csv(paste0(filepath_in, "C_19.csv"))
C_22 <- read_csv(paste0(filepath_in, "C_22.csv"))
C_25 <- read_csv(paste0(filepath_in, "C_25.csv"))
# C_26 <- read_csv(paste0(filepath_in, "C_26.csv"))
# C_28 <- read_csv(paste0(filepath_in, "C_28.csv"))
C_29 <- read_csv(paste0(filepath_in, "C_29.csv"))
C_31 <- read_csv(paste0(filepath_in, "C_31.csv"))
C_36 <- read_csv(paste0(filepath_in, "C_36.csv"))
C_37 <- read_csv(paste0(filepath_in, "C_37.csv")) #15 stops here
# C_38 <- read_csv(paste0(filepath_in, "C_38.csv"))
# C_40 <- read_csv(paste0(filepath_in, "C_40.csv")) 
# C_41 <- read_csv(paste0(filepath_in, "C_41.csv")) 

# Merge all controls
mergedC <-
  full_join(C_4, C_5) |>
  full_join(C_6) |>
  full_join(C_8) |>
  full_join(C_12) |>
  full_join(C_13) |>
  full_join(C_14) |>
  full_join(C_15) |>
  # full_join(C_16) |>
  # full_join(C_18) |>
  full_join(C_19) |>
  full_join(C_22) |>
  full_join(C_25) |>
  # full_join(C_26) |>
  # full_join(C_28) |>
  full_join(C_29) |>
  full_join(C_31) |>
  full_join(C_36) |>
  full_join(C_37)

mergedC <- 
  mergedC |> 
  pivot_longer(cols = 3:14,
               names_to = c("trialType", "validity"),
               names_sep = "_",
               values_to = "percentage")

# Save C merged dataset
write_csv(mergedC, paste0(filepath_out, "mergedC.csv"))

# # OPTIONAL
# mergedC_OL <- 
#   mergedC |> 
#   filter(!rtDet %in% outlierListC[]) |> 
#   pivot_longer(cols = 3:14,
#                names_to = c("trialType", "validity"),
#                names_sep = "_",
#                values_to = "percentage")
# 
# # Save C merged dataset
# write_csv(mergedC_OL, paste0(filepath_out, "mergedC_OL.csv"))
```

## 3) MA Read Dataset
```{r, message=FALSE, warning=FALSE}
# # Read all MA participants
# MA_7 <- read_csv(paste0(filepath_in, "MA_7.csv"))
# MA_9 <- read_csv(paste0(filepath_in, "MA_9.csv"))
# MA_11 <- read_csv(paste0(filepath_in, "MA_11.csv"))
MA_20 <- read_csv(paste0(filepath_in, "MA_20.csv"))
# MA_21 <- read_csv(paste0(filepath_in, "MA_21.csv"))
# MA_24 <- read_csv(paste0(filepath_in, "MA_24.csv"))
# MA_27 <- read_csv(paste0(filepath_in, "MA_27.csv"))
# MA_30 <- read_csv(paste0(filepath_in, "MA_30.csv"))
# MA_33 <- read_csv(paste0(filepath_in, "MA_33.csv"))
# MA_34 <- read_csv(paste0(filepath_in, "MA_34.csv"))
# MA_35 <- read_csv(paste0(filepath_in, "MA_35.csv"))
# MA_39 <- read_csv(paste0(filepath_in, "MA_39.csv"))
mergedMA<-MA_20
# # Merge to 1 dataset
# mergedMA <- full_join(MA_7, MA_9) |>
#             full_join(MA_11) |>
#             full_join(MA_20) |>
#             full_join(MA_21) |>
#             full_join(MA_24) |>
#             full_join(MA_27) |>
#             full_join(MA_30) |>
#             full_join(MA_33) |>
#             full_join(MA_34) |>
#             full_join(MA_35)

mergedMA <- 
  mergedMA |> 
  pivot_longer(cols = 3:14,
               names_to = c("trialType", "validity"),
               names_sep = "_",
               values_to = "percentage")

# Save C merged dataset
write_csv(mergedMA, paste0(filepath_out, "mergedMA.csv"))

# # OPTIONAL
# mergedMA_OL <- 
#   mergedMA |> 
#   filter(!rtDet %in% outlierListMA[]) |> 
#   pivot_longer(cols = 3:14,
#                names_to = c("trialType", "validity"),
#                names_sep = "_",
#                values_to = "percentage")
# 
# # Save C merged dataset
# write_csv(mergedMA_OL, paste0(filepath_out, "mergedMA_OL.csv"))
```

# 5) MO Read Data Set
```{r, message=FALSE, warning=FALSE}
# MO_2 <- read_csv(paste0(filepath_in, "MO_2.csv"))
# MO_3 <- read_csv(paste0(filepath_in, "MO_3.csv"))
MO_10 <- read_csv(paste0(filepath_in, "MO_10.csv"))
# MO_17 <- read_csv(paste0(filepath_in, "MO_17.csv"))
# MO_32 <- read_csv(paste0(filepath_in, "MO_32.csv"))
mergedMO<-MO_10
# # Merge to 1 dataset
# mergedMO <- full_join(MO_2, MO_3) |> 
#             full_join(MO_10) |>
#             full_join(MO_17) |>
#             full_join(MO_32)

mergedMO <- 
  mergedMO |> 
  pivot_longer(cols = 3:14,
               names_to = c("trialType", "validity"),
               names_sep = "_",
               values_to = "percentage")

# Save C merged dataset
write_csv(mergedMO, paste0(filepath_out, "mergedMO.csv"))

# # OPTIONAL
# mergedMO_OL <-
#   mergedMO |> 
#   filter(!rtDet %in% outlierListMO[]) |> 
#   pivot_longer(cols = 3:14,
#                names_to = c("trialType", "validity"),
#                names_sep = "_",
#                values_to = "percentage")
# 
# # Save C merged dataset
# write_csv(mergedMO_OL, paste0(filepath_out, "mergedMO_OL.csv"))
```

# 7) Merge Migraines (Optional)
```{r, message=FALSE, warning=FALSE}
mergedM <- full_join(mergedMO, mergedMA) |> 
  mutate(group = recode(group, "MO" = "M",
                               "MA" = "M"))
write.csv(mergedM, paste0(filepath_out, "mergedM.csv"))
```

# 8) Combine all datasets
```{r, message=FALSE, warning=FALSE}
allGroups <- full_join(mergedC, mergedM)
write.csv(allGroups, paste0(filepath_out, "allGroups.csv"))
```

# 9) ONLY ACCURACY DATA
```{r}

```

# 9) Combine all OL datasets
```{r, message=FALSE, warning=FALSE}
# mergedM_OL <- full_join(mergedMO_OL, mergedMA_OL) |> 
#   mutate(group = recode(group, "MO" = "M",
#                                "MA" = "M"))
# write.csv(mergedM_OL, paste0(filepath_out, "mergedM_OL.csv"))
# 
# allGroups_OL <- full_join(mergedC_OL, mergedM_OL)
# write.csv(allGroups_OL, paste0(filepath_out, "allGroups_OL.csv"))
```










