---
title: "BEH4_stats"
author: "Leonardo Sutandi"
date: "2025-03-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lme4)
library(ggResidpanel) #https://goodekat.github.io/ggResidpanel/articles/introduction.html
library(rstatix)
# library(knitr)
# library(kableExtra)
```

# Load Dataset
```{r, message=FALSE, warning=FALSE}

filepath <- "C:/R/exp_1/results/BEH/merged_group_dataset/"

mergedC <- read_csv(paste0(filepath, "mergedC.csv"))
mergedMA <- read_csv(paste0(filepath, "mergedMA.csv"))
mergedMO <- read_csv(paste0(filepath, "mergedMO.csv"))
mergedM <- read_csv(paste0(filepath, "mergedM.csv"))
allGroups <- read_csv(paste0(filepath, "allGroups.csv"))

# Data to work
data <- allGroups
```

# Descriptives
```{r}

data |>
  group_by(validity, trialType, group) |>
  get_summary_stats(rtDet, type = "mean_sd")

  # flextable(cwidth = .95) |>
  # fontsize(size = 8) |>
  # fontsize(size = 10, part = "header") |>
  # 
  # set_header_labels(validity = "Validity",
  #                   targetLR = "Left/Right Target",
  #                   trialType = "Gratings",
  #                   variable = "Variable")
```

# LMM Instruction

lmer(outcome ~ 1 + predictor + (1|participant) + (1|item), data = data)

random effects = interior parentheses (1|X) > participant, item; left of | vary by grouping factor on right |
fixed effect =  not in parentheses > outcome, predictor

Statistical plan
separated for each attentional orienting groups - cuePos (Left vs Right) for each ROI:

- Random effects: participants
- Fixed effects: Groups (C vs MA vs MO), trialType (NG vs G)


# Filter (CURRENTLY RECODE)

```{r, message=FALSE, warning=FALSE}
data <- 
  data |>
  mutate(group = recode(group, "MA" = "M", # mix migraine groups
                            "MO" = "M"),
         Acc = recode(correctAcc, "correct"=0, "incorrect"=1))  |> 
  # select(id, group, trialType, validity, correctDet, rtDet) |>
  filter(correctDet == "correct", rtDet >0.2)

data$id <- as.factor(data$id)
data$group <- as.factor(data$group)
# data$fixJitData <- as.factor(data$fixJitData)
data$trialType <- as.factor(data$trialType)
data$validity <- as.factor(data$validity)
# data$id <- as.factor(data$cuePos)
# data$targetLR <- as.factor(data$targetLR)
# data$correctAcc <- as.factor(data$correctAcc)

# fullData <- fullData |> mutate(log_rt = log(rtDet))
```

# Vsualise hist RT
```{r}
hist(data$rtDet)
```


# Visualise Data Per Subject
```{r, message=FALSE, warning=FALSE}

perSubject <- 
  data |>
  filter(group == "C") |>
  ggplot(aes(x = validity, y = rtDet)) +
  geom_boxplot() +
  stat_summary(fun.y = mean, geom = "line", aes(group=1), colour = "red") +
  # stat_smooth(method= 'lm', se = FALSE) +
  scale_x_discrete(limits = c("valid", "neutral", "invalid")) +
  facet_wrap(~id)
print(perSubject)

```


# Behavioural Data Analysis

```{r, message=FALSE, warning=FALSE}

fullModel <- lmer(rtDet ~ trialType * validity * group + (1|id), 
                data = data,
                REML=F)
summary(fullModel)
resid_panel(fullModel, smoother = TRUE, qqbands = TRUE)

reducedModel <- lmer(rtDet ~ trialType * validity + (1|id), 
                data = data,
                REML=F)
summary(reducedModel)
resid_panel(reducedModel, smoother = TRUE, qqbands = TRUE)

# summary(lmm_beh)$coefficients
anova(fullModel, reducedModel)
```

# Fitting Gamma
```{r}
# Using glmer() link function does not transform the raw data, but transform the prediction.

# Full Gamma Model
full_bino <- glmer(Acc ~ trialType * validity * group + (1|id),
                   data = data,
                   family = binomial(link = "logit"))
summary(full_bino)
resid_panel(fullGamma, smoother = TRUE, qqbands = TRUE)

# Reduced Model w/o Group Factor
reducedGamma <- glmer(rtDet ~ trialType * validity + (1|id),
                   data = data,
                   family = Gamma(link = "log"))
summary(reducedGamma)
resid_panel(reducedGamma, smoother = TRUE, qqbands = TRUE)

# Reduced Model w/o trialType Factor
reducedGamma2 <- glmer(rtDet ~ validity + (1|id),
                   data = data,
                   family = Gamma(link = "log"))
summary(reducedGamma2)
resid_panel(reducedGamma2, smoother = TRUE, qqbands = TRUE)

# flexplot::model.comparison(fullGamma, reducedGamma)

# flexplot(formula =rtDet~validity|group, data=data, method="Gamma" )
# var<-as.data.frame(VarCorr(fullGamma))
# varPerc <- (var$vcov[1])/sum(var$vcov)

#library(effects) > plot(allEffects(model), main = "") > 
```


# Model Comparison
```{r}
# fullGamma vs w/o group (i.e. does group play a role in RT)
anova(fullGamma, reducedGamma)
# fullGamma vs w/o trialType (i.e. does trialType play a role in RT)
anova(reducedGamma, reducedGamma2)
```






































# Residuals
```{r}
# # Choose model to plot
# model <- fullModel
# 
# residuals <- residuals(model)
# 
# qq <- qqnorm(residuals)
# qqline(residuals) 
# res_plot <- plot(fitted(model), residuals, main = "Residual Plot")
# abline(0,0)
# hist_qq <- hist(residuals, breaks = 40, main = "Histogram of Residuals", xlab = "Residuals")
# 
# qq
# res_plot
# hist_qq
```

# Introduce slope to lmer
```{r}
lmm_beh_2 <- lmer(rtDet ~ 1 + trialType + validity + group + (1 + group|id), data = fullData, REML = F)
summary(lmm_beh_2)
```

# anova
```{r, message=FALSE, warning=FALSE}
anova_beh <- aov(rtDet ~ validity * trialType * group, 
                 data = fullData)
summary(anova_beh)
```

# Anova Post Hoc
```{r}
post_hoc <- Post
```


# ANOVA rstatix
```{r}
anova_rstatix <- rstatix::anova_test(data = fullData,
                                     formula = rtDet ~ validity * trialType * group,
                                     dv = rtDet,
                                     wid = id,
                                     between = c(group),
                                     within = c(validity, trialType),
                                     effect.size = "pes") #"Effect Size (ƞ2p)"
get_anova_table(anova_rstatix, correction = "GG")

# #Cohen's D Benchmarks
# #.01: Small effect size
# #.06: Medium effect size
# #.14 or higher: Large effect size
```


# afex::aov
```{r}
library(afex)

aov_ez(id = "id", 
       dv = "rtDet", 
       data = fullData, 
       between = c("group"), 
       within = c("validity", "trialType"),
       fun_aggregate = mean,
       type = 3)
```























# Steven Luke (2016) R code for p values in lmer
```{r}
###R Code for implementing the recommended methods for obtaining p-values in lme4.

##Using R Package lmerTest to implement Satterthwaite or Kenward-Roger approximations.

library(lmerTest) #Package must be installed first

Model.REML = lmer(Response ~ Condition + (1 + Condition | Subject) + (1 + Condition | Item), REML = TRUE,

data = MyData) #Fitting a model using REML

anova(Model.REML) #Performs F test on fixed effects using Satterthwaite approximation

anova(Model.REML, ddf = “Kenward-Roger”) #Performs F test using Kenward-Roger approximation

summary(Model.REML) #gives model output with estimated df and p values using Satterthwaite

summary(Model.REML, ddf = “Kenward-Roger”) #gives model output using Kenward-Roger

##Using Package afex to implement the Kenward-Roger approximation

library(afex) #Package must be installed first

Model.REML.afex.KR = mixed(Response ~ Condition + (1 + Condition | Subject) + (1 + Condition | Item),

data = MyData, REML = TRUE, method = “KR”) #Tests fixed effects using Kenward-Roger

Model.REML.afex.KR #Returns ANOVA table with F test on fixed effects using Kenward-Roger

Model.ML.afex.LRT = mixed(Response ~ Condition + (1 + Condition | Subject) + (1 + Condition | Item),

data = MyData, REML = FALSE, method = “LRT”) #Performs likelihood ratio tests

Model.ML.afex.LRT #Returns results of Likelihood Ration Test on Fixed Effect.

#Using LRTs is not recommended unless both number of subjects and number of items are quite large (40+)

#Note 1: This code assumes that you are attempting to obtain p-values after having settled on a final random #effects structure. Models shown here are maximal, with all possible random slopes/intercepts.
```




















