---
title: "Behavioural Data"
author: "Leonardo Sutandi"
date: "2025-04-03"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Stats
library(lme4)
library(ggResidpanel) #https://goodekat.github.io/ggResidpanel/articles/introduction.html
library(rstatix)
# Plotting
library(cowplot)
# library(flextable)
library(patchwork)
# Table Format
library(kableExtra)
library(gtsummary)
# Main
library(tidyverse)
```


# Part 1: Reaction Time >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
```{r, include=F, message=FALSE, warning=FALSE, echo=F}

filepath <- "C:/R/exp_1/results/BEH/merged_group_dataset/"

mergedC <- read_csv(paste0(filepath, "mergedC.csv"))
mergedMA <- read_csv(paste0(filepath, "mergedMA.csv"))
mergedMO <- read_csv(paste0(filepath, "mergedMO.csv"))
mergedM <- read_csv(paste0(filepath, "mergedM.csv"))
allGroups <- read_csv(paste0(filepath, "allGroups.csv"))

# allGroups$id <- as.factor(allGroups$id)
# allGroups$group <- as.factor(allGroups$group)
# # allGroups$fixJitData <- as.factor(allGroups$fixJitData)
# allGroups$trialType <- as.factor(allGroups$trialType)
# allGroups$validity <- as.factor(allGroups$validity)
# # allGroups$id <- as.factor(allGroups$cuePos)
# # allGroups$targetLR <- as.factor(allGroups$targetLR)
# allGroups$correctDet <- as.factor(allGroups$correctDet)
```

## Control
```{r, message=FALSE, warning=FALSE, fig.title="title", echo=F}

data <- 
  mergedC |> 
  filter(trialType == "NG",  # Only want NoGrat
         correctDet == "correct") # Only want correct response

# Set plot contents
noGratRt_C <- 
  ggplot(data, aes(validity, rtDet, fill = validity)) + 
  # Set whiskers
  stat_boxplot(geom = 'errorbar', 
               width = 0.3, 
               coef = 1.5) +
  # Set plot design
  geom_jitter(aes(color = validity), #aes(col = id),
              width = 0.3, 
              alpha = 0.05) +
  # scale_color_manual(values=c("indianred3", "limegreen", "dodgerblue"))  +
  guides(color = FALSE) +
  geom_boxplot(width = 0.5,
               alpha = 1,
               outlier.shape = NaN) +
  
  # Set mean
  stat_summary(fun.y = mean, 
               geom = "line",
               aes(group = 1),
               size = 0.8,
               colour = "gray50",
               show.legend = F) +  
  stat_summary(fun = mean,
               geom = "point",
               shape = 16,
               size = 1.5,
               colour = "black",
               show.legend = F)  +
  # Set major labels (title, Y, X axis)
  labs(title = "No Gratings",
       x = " ",
       y = "RT (Secs)") +
  # Rename each X axis character label
  scale_x_discrete(limits = c("invalid", "neutral", "valid"),
                   labels = c("Invalid", "Neutral", "Valid")) +
  # Set Y axis range
  ylim(0, 2) +
  # Set colour
  scale_fill_manual(values=c("coral", "seagreen1", "cadetblue1")) +
  # scale_fill_manual(values=c("gray", "gray", "gray")) +
  # Plot theme
  theme_bw() +
  # Remove legend
  guides(fill=FALSE)


# Gratings
data <- 
  mergedC |> 
  filter(trialType == "G",
         correctDet == "correct")

# Set plot contents
gratRt_C <- 
  ggplot(data, 
         aes(validity, rtDet, fill = validity))  + 
  # Set whiskers
  stat_boxplot(geom = 'errorbar', 
               width = 0.3) +
  # Set plot design
  geom_jitter(aes(color=validity), 
              width = 0.3, 
              alpha = 0.05) +
  scale_color_manual(values=c("indianred3", "limegreen", "dodgerblue"))  +
  guides(color=FALSE) +
  geom_boxplot(width = 0.5,
               alpha = 1, 
               outlier.shape = NaN) +
  # Set mean
  stat_summary(fun.y = mean, 
               geom = "line",
               aes(group = 1),
               size = 0.8,
               colour = "gray50",
               show.legend = F) +  
  stat_summary(fun = mean,
               geom = "point",
               shape = 16,
               size = 1.5,
               colour = "black",
               show.legend = F)  +
  # Set major labels (title, Y, X axis)
  labs(title = "Gratings",
       x = "",
       y = "RT (Secs)") +
  # Rename each X axis character label
  scale_x_discrete(limits = c("invalid", "neutral", "valid"),
                   labels = c("Invalid", "Neutral", "Valid")) +
  # Set Y axis range
  ylim(0, 2) +
  # Set colour
  scale_fill_manual(values=c("coral", "seagreen1", "cadetblue1")) +
  # Plot theme
  theme_bw() +
  # Remove legend
  guides(fill=FALSE)

# mergedC_plot <- plot_grid(noGratRt_C, gratRt_C, labels = c("A", "B"), ncol = 2, nrow = 1)
# title <- ggdraw() + 
#   draw_label(
#     "All Control - RT Correct Detection",
#     fontface = 'bold',
#     x = 0,
#     hjust = 0) +
#   theme(plot.margin = margin(0, 0, 0, 3))
# mergedC_plot <- plot_grid(title, mergedC_plot, ncol = 1, nrow = 2, rel_heights = c(0.05, 1))
# ggsave("C:/MATLAB/exp_1/results/figures/mergedC_plot.jpg", mergedC_plot, height = 5)
# print(mergedC_plot)

mergedC_plot <- noGratRt_C + gratRt_C + 
  plot_annotation(title = "RT Correct Detection - Control")
ggsave("C:/MATLAB/exp_1/results/figures/mergedC_plot.jpg", mergedC_plot, height = 5)
print(mergedC_plot)

```

## Descriptives
```{r, echo=F}
mergedC |> filter(correctDet == "correct")|>
  group_by(validity, trialType, group) |>
  rstatix::get_summary_stats(rtDet, type = "mean_sd")
```

## Migraine
```{r, message=FALSE, warning=FALSE, echo=F}

data <- 
  mergedM |> 
  filter(trialType == "NG",  # Only want NoGrat
         correctDet == "correct") # Only want correct response

# Set plot contents
noGratRt_M <- 
  ggplot(data, aes(validity, rtDet, fill = validity)) + 
  # Set whiskers
  stat_boxplot(geom = 'errorbar', 
               width = 0.3, 
               coef = 1.5) +
  # Set plot design
  geom_jitter(aes(colour = validity),
              width = 0.3, 
              alpha = 0.05) +
  scale_color_manual(values=c("indianred3", "limegreen", "dodgerblue"))  +
  guides(color = FALSE) +
  geom_boxplot(width = 0.5,
               alpha = 1,
               outlier.shape = NaN) +
  
  # Set mean
  stat_summary(fun.y = mean, 
               geom = "line",
               aes(group = 1),
               size = 0.8,
               colour = "gray50",
               show.legend = F) +  
  stat_summary(fun = mean,
               geom = "point",
               shape = 16,
               size = 1.5,
               colour = "black",
               show.legend = F)  +
  # Set major labels (title, Y, X axis)
  labs(title = "No Gratings",
       x = "",
       y = "RT (Secs)") +
  # Rename each X axis character label
  scale_x_discrete(limits = c("invalid", "neutral", "valid"),
                   labels = c("Invalid", "Neutral", "Valid")) +
  # Set Y axis range
  ylim(0, 2) +
  # Set colour
  scale_fill_manual(values=c("coral", "seagreen1", "cadetblue1")) +
  # Plot theme
  theme_bw() +
  # Remove legend
  guides(fill=FALSE)

# Gratings
data <- 
  mergedM |> 
  filter(trialType == "G",  # Only want NoGrat
         correctDet == "correct") # Only want correct response

# Set plot contents
gratRt_M <- 
  ggplot(data, aes(validity, rtDet, fill = validity)) + 
  # Set whiskers
  stat_boxplot(geom = 'errorbar', 
               width = 0.3, 
               coef = 1.5) +
  # Set plot design
  geom_jitter(aes(colour = validity),
              width = 0.3, 
              alpha = 0.05) +
  scale_color_manual(values=c("indianred3", "limegreen", "dodgerblue"))  +
  guides(color = FALSE) +
  geom_boxplot(width = 0.5,
               alpha = 1,
               outlier.shape = NaN) +
  
  # Set mean
  stat_summary(fun.y = mean, 
               geom = "line",
               aes(group = 1),
               size = 0.8,
               colour = "gray50",
               show.legend = F) +  
  stat_summary(fun = mean,
               geom = "point",
               shape = 16,
               size = 1.5,
               colour = "black",
               show.legend = F)  +
  # Set major labels (title, Y, X axis)
  labs(title = "Gratings",
       x = "",
       y = "RT (Secs)") +
  # Rename each X axis character label
  scale_x_discrete(limits = c("invalid", "neutral", "valid"),
                   labels = c("Invalid", "Neutral", "Valid")) +
  # Set Y axis range
  ylim(0, 2) +
  # Set colour
  scale_fill_manual(values=c("coral", "seagreen1", "cadetblue1")) +
  # Plot theme
  theme_bw() +
  # Remove legend
  guides(fill=FALSE)


# mergedMA_plot <- plot_grid(noGratRt_MA, gratRt_MA, labels=c("A", "B"), ncol = 2, nrow = 1)
# title <- ggdraw() + 
#   draw_label(
#     "All Migraine - RT Correct Detection",
#     fontface = 'bold',
#     x = 0,
#     hjust = 0) +
#   theme(plot.margin = margin(0, 0, 0, 3))
# mergedMA_plot <- plot_grid(title, mergedMA_plot, ncol = 1, nrow = 2, rel_heights = c(0.05, 1))
# ggsave("C:/MATLAB/exp_1/results/figures/mergedMA_plot.png", mergedMA_plot, height = 5)
# print(mergedMA_plot)

mergedM_plot <- noGratRt_M + gratRt_M + 
  plot_annotation(title = "RT Correct Detection - All Migraine")
ggsave("C:/MATLAB/exp_1/results/figures/mergedM_plot.jpg", mergedM_plot, height = 5)
print(mergedM_plot)

```

## Descriptives
```{r, echo=F}
mergedM |> filter(correctDet == "correct")|>
  group_by(validity, trialType, group) |>
  rstatix::get_summary_stats(rtDet, type = "mean_sd")
```

## Control vs Migraine
```{r, message=F, warning=F, echo=F}
# gratComp <- plot_grid(noGratRt_C, noGratRt_MA, gratRt_C, gratRt_MA, labels=c("NG_C", "NG_M", "G_C", "G_M"), ncol = 2, nrow = 1)
# title <- ggdraw() + 
#   draw_label(
#     "Trial Comparison Between Groups",
#     fontface = 'bold',
#     x = 0,
#     hjust = 0) +
#   theme(plot.margin = margin(0, 0, 0, 3))
# gratComp <- plot_grid(title, gratComp, ncol = 1, nrow = 2, rel_heights = c(0.05, 1))
# ggsave("C:/MATLAB/exp_1/results/figures/mergedMA_plot.png", mergedMA_plot, height = 5)
# print(gratComp)

# ggarrange(noGratRt_C, noGratRt_MA, gratRt_C, gratRt_MA, labels=c("NG_C", "NG_M", "G_C", "G_M"), ncol = 2, nrow = 2)

NG_comp <- noGratRt_C + noGratRt_M +
  plot_annotation(title = "No Gratings RT Correct Detection -  Control (Left) vs Migraine (Right)")
G_comp <- gratRt_C + gratRt_M +
  plot_annotation(title = "Gratings RT Correct Detection -  Control (Left) vs Migraine (Right)")

print(NG_comp)
print(G_comp)

```


# Statistics Descriptives
```{r}
# working data
data <- allGroups

# Descriptives
data |>
  group_by(validity, trialType, group) |>
  rstatix::get_summary_stats(rtDet, type = "mean_sd")
```

## Data Configuration
```{r}
data <- 
  data |>
  mutate(group = recode(group, "MA" = "M", # mix migraine groups
                            "MO" = "M"),
         Acc = recode(correctAcc, "correct"=0, "incorrect"=1))  |> 
  # select(id, group, trialType, validity, correctDet, rtDet) |>
  filter(correctDet == "correct", rtDet >0.2)

data$id <- as.factor(data$id)
data$group <- as.factor(data$group)
# data$fixJitData <- as.factor(data$fixJitData)
data$trialType <- as.factor(data$trialType)
data$validity <- as.factor(data$validity)
```

## Full GLMM (Gamma - link: Log) Model
```{r}
rt_model <- 
  glmer(rtDet ~ trialType * validity * group + (1|id),
        data = data,
        family = Gamma(link = "log"))

summary(rt_model)
# tbl_regression(rt_model,
#                intercept = T,
#                pvalue_fun = label_style_pvalue(digits =2)) |> 
#   # add_global_p() |> 
#   bold_p(t = 0.05) |> 
#   bold_labels() |> 
#   italicize_levels()

resid_panel(rt_model, smoother = TRUE, qqbands = TRUE)
```

## Reduced GLMM (Gamma - link: Log) Model (w/o Group Factor)
```{r}
# Reduced Model w/o Group Factor
rt_model_reduced1 <- 
  glmer(rtDet ~ trialType * validity + (1|id),
        data = data,
        family = Gamma(link = "log"))
summary(rt_model_reduced1)
resid_panel(rt_model_reduced1, smoother = TRUE, qqbands = TRUE)

```

## Model Comparison
```{r}

# Does group significantly affect RT?
anovaRt <- 
  anova(rt_model_reduced1, rt_model)  |> 
  mutate(model = c("Reduced Model", "Full Model"), .before = 1)
  
#rt_table <- 
  anovaRt |>
  kbl() |>
  kable_classic(full_width = F,
                html_font = "Cambria")


  tbl_summary(anovaRt,
            include = c("AIC", "BIC", "Chisq", "Df", "Pr(>Chisq)"), 
            by = "model")

```

```{r}
# Full Model
mod1 <-
tbl_regression(rt_model,
               intercept = T,
               pvalue_fun = label_style_pvalue(digits =2)) |> 
  # add_global_p() |> 
  bold_p(t = 0.05) |> 
  bold_labels() |> 
  italicize_levels()
# Reduced Model
mod2 <-
  tbl_regression(rt_model_reduced1,
               intercept = T,
               pvalue_fun = label_style_pvalue(digits =2)) |> 
  # add_global_p() |> 
  bold_p(t = 0.05) |> 
  bold_labels() |> 
  italicize_levels()
# Merge Model
tbl_merge(tbls = list(mod1, mod2),
          tab_spanner = c("**Full Model**", "**Reduced Model**")) |> 
  as_gt() |> 
  gt::gtsave(filename = "rt_stats.png",
             path = "C:/MATLAB/exp_1/results/figures")

```

_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________
_______________________________________________________________________________________________________________________

# Part 2: Accuracy >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
```{r, warning=F, message=F, echo=F}
# Accuracy needs percentage allGroups
filepath2 <- "C:/R/exp_1/results/BEH/merged_group_dataset_acc/"

mergedC <- read_csv(paste0(filepath2, "mergedC.csv"))
mergedMA <- read_csv(paste0(filepath2, "mergedMA.csv"))
mergedMO <- read_csv(paste0(filepath2, "mergedMO.csv"))
mergedM <- read_csv(paste0(filepath2, "mergedM.csv"))
allGroups <- read_csv(paste0(filepath2, "allGroups.csv"))

# mergedC_OL <- read_csv(paste0(filepath2, "mergedC_OL.csv"))
# mergedMA_OL <- read_csv(paste0(filepath2, "mergedMA_OL.csv"))
# mergedMO_OL <- read_csv(paste0(filepath2, "mergedMO_OL.csv"))
# mergedM_OL <- read_csv(paste0(filepath2, "mergedM_OL.csv"))
# allGroups_OL <- read_csv(paste0(filepath2, "allGroups_OL.csv"))

```

## Control
```{r, message=F, warning=F, echo=F}

# NG >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
data <- 
  allGroups |> 
  filter(group == "C")

# Set plot content
c_acc <- 
  ggplot(data, aes(validity, percentage)) + 
  # Set Bars
  geom_bar(aes(fill = validity),
           position = "dodge",
           stat = "summary",
           fun.y = "mean",
           width = 0.7) +
  # Set whiskers
  stat_boxplot(geom = 'errorbar', 
               width = 0.1, 
               coef = 1.5) +
  # Set plot design
  geom_jitter(#aes(col = id),
              width = 0.3,
              alpha = 0.3) +
  # scale_color_manual(values=c("indianred3", "limegreen", "dodgerblue"))  +
  guides(color = FALSE) +
  geom_boxplot(width = 0.2,
               alpha = 1,
               outlier.shape = NaN) +
  
  # Set mean
  # stat_summary(fun.y = mean, 
  #              geom = "line",
  #              aes(group = 1),
  #              size = 0.8,
  #              colour = "gray50",
  #              show.legend = F) +  
  # stat_summary(fun = mean,
  #              geom = "point",
  #              shape = 16,
  #              size = 1.5,
  #              colour = "black",
  #              show.legend = F)  +
  # Set major labels (title, Y, X axis)
  labs(title = "Control",
       x = "Validity",
       y = "Accuracy (%)") +
  # Rename each X axis character label
  # scale_x_discrete(limits = c("invalid", "valid"),
  #                  labels = c("Invalid", "Valid")) +
  # Set Y axis range
  ylim(0, 101) +
  # Set colour
  # scale_fill_manual(values=c("coral", "cadetblue1")) +
  # scale_fill_manual(values=c("gray", "gray")) +
  # Plot theme
  theme_bw() +
  # Remove legend
  guides(fill=F)

print(c_acc)
```

## Migraine
```{r, message=F, warning=F, echo=F}

# NG >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
data <- 
  allGroups |> 
  filter(group == "M")

# Set plot content
m_acc <- 
  ggplot(data, aes(validity, percentage)) + 
  # Set Bars
  geom_bar(aes(fill = validity),
           position = "dodge",
           stat = "summary",
           fun.y = "mean",
           width = 0.7) +
  # Set whiskers
  stat_boxplot(geom = 'errorbar', 
               width = 0.1, 
               coef = 1.5) +
  # Set plot design
  geom_jitter(#aes(col = id),
              width = 0.3,
              alpha = 0.3) +
  # scale_color_manual(values=c("indianred3", "limegreen", "dodgerblue"))  +
  guides(color = FALSE) +
  geom_boxplot(width = 0.2,
               alpha = 1,
               outlier.shape = NaN) +
  
  # Set mean
  # stat_summary(fun.y = mean, 
  #              geom = "line",
  #              aes(group = 1),
  #              size = 0.8,
  #              colour = "gray50",
  #              show.legend = F) +  
  # stat_summary(fun = mean,
  #              geom = "point",
  #              shape = 16,
  #              size = 1.5,
  #              colour = "black",
  #              show.legend = F)  +
  # Set major labels (title, Y, X axis)
  labs(title = "Migraine",
       x = "Validity",
       y = "Accuracy (%)") +
  # Rename each X axis character label
  # scale_x_discrete(limits = c("invalid", "valid"),
  #                  labels = c("Invalid", "Valid")) +
  # Set Y axis range
  ylim(0, 101) +
  # Set colour
  # scale_fill_manual(values=c("coral", "cadetblue1")) +
  # scale_fill_manual(values=c("gray", "gray")) +
  # Plot theme
  theme_bw() +
  # Remove legend
  guides(fill=F)

print(m_acc)
```

## Control vs Migraine (all data)
```{r, message=F, warning=F, echo=F}
all_acc <- c_acc + m_acc +
  plot_annotation(title = "All Data")
# ggsave("C:/MATLAB/exp_1/results/figures/mergedC_plot.png", mergedC_plot, height = 5)
print(all_acc)
```


## NG Overall (Control vs Migraine)
```{r, message=F, warning=F, echo=F}

tT = "NG"

# Valid >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
data <- 
  allGroups |> 
  filter(trialType == tT,
         validity == "valid")

# Set plot contents
ng_valid <- 
  ggplot(data, aes(group, percentage)) + 
  # Set Bars
  geom_bar(aes(fill = group),
           position = "dodge",
           stat = "summary",
           fun.y = "mean",
           width = 0.7) +
  # Set whiskers
  stat_boxplot(geom = 'errorbar', 
               width = 0.1, 
               coef = 1.5) +
  # Set plot design
  geom_jitter(#aes(col = id),
              width = 0.3,
              alpha = 0.3) +
  # scale_color_manual(values=c("indianred3", "limegreen", "dodgerblue"))  +
  guides(color = FALSE) +
  geom_boxplot(width = 0.2,
               alpha = 1,
               outlier.shape = NaN) +
  
  # Set mean
  # stat_summary(fun.y = mean, 
  #              geom = "line",
  #              aes(group = 1),
  #              size = 0.8,
  #              colour = "gray50",
  #              show.legend = F) +  
  # stat_summary(fun = mean,
  #              geom = "point",
  #              shape = 16,
  #              size = 1.5,
  #              colour = "black",
  #              show.legend = F)  +
  # Set major labels (title, Y, X axis)
  labs(title = "Valid",
       x = "",
       y = "Accuracy (%)") +
  # Rename each X axis character label
  # scale_x_discrete(limits = c("invalid", "valid"),
  #                  labels = c("Invalid", "Valid")) +
  # Set Y axis range
  ylim(0, 101) +
  # Set colour
  # scale_fill_manual(values=c("coral", "cadetblue1")) +
  # scale_fill_manual(values=c("gray", "gray")) +
  # Plot theme
  theme_bw() +
  # Remove legend
  guides(fill=F)

# Invalid >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
data <-
  allGroups |>
  filter(trialType == tT,
         validity == "invalid")

# Set plot contents
ng_invalid <-
  ggplot(data, aes(group, percentage)) +
  # Set Bars
  geom_bar(aes(fill = group),
           position = "dodge",
           stat = "summary",
           fun.y = "mean",
           width = 0.7) +
  # Set whiskers
  stat_boxplot(geom = 'errorbar',
               width = 0.1,
               coef = 1.5) +
  # Set plot design
  geom_jitter(#aes(col = id),
              width = 0.3,
              alpha = 0.3) +
  # scale_color_manual(values=c("indianred3", "limegreen", "dodgerblue"))  +
  guides(color = FALSE) +
  geom_boxplot(width = 0.2,
               alpha = 1,
               outlier.shape = NaN) +

  labs(title = "Invalid",
       x = "",
       y = "") +
  ylim(0, 101) +
  # Plot theme
  theme_bw() +
  # Remove legend
  guides(fill=FALSE)

# Neutral >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
data <-
  allGroups |>
  filter(trialType == tT,
         validity == "neutral")

# Set plot contents
ng_neutral <-
  ggplot(data, aes(group, percentage)) +
  # Set Bars
  geom_bar(aes(fill = group),
           position = "dodge",
           stat = "summary",
           fun.y = "mean",
           width = 0.7) +
  # Set whiskers
  stat_boxplot(geom = 'errorbar',
               width = 0.1,
               coef = 1.5) +
  # Set plot design
  geom_jitter(#aes(col = id),
              width = 0.3,
              alpha = 0.3) +
  # scale_color_manual(values=c("indianred3", "limegreen", "dodgerblue"))  +
  guides(color = FALSE) +
  geom_boxplot(width = 0.2,
               alpha = 1,
               outlier.shape = NaN) +
  labs(title = "Neutral",
       x = "",
       y = "") +
  # Set Y axis range
  ylim(0, 101) +
  # Plot theme
  theme_bw() 
  

# mergedC_plot <- plot_grid(noGratRt_C, gratRt_C, labels = c("A", "B"), ncol = 2, nrow = 1)
# title <- ggdraw() + 
#   draw_label(
#     "All Control - RT Correct Detection",
#     fontface = 'bold',
#     x = 0,
#     hjust = 0) +
#   theme(plot.margin = margin(0, 0, 0, 3))
# mergedC_plot <- plot_grid(title, mergedC_plot, ncol = 1, nrow = 2, rel_heights = c(0.05, 1))
# ggsave("C:/MATLAB/exp_1/results/figures/mergedC_plot.png", mergedC_plot, height = 5)
# print(mergedC_plot)

ng_acc <- ng_valid + ng_invalid + ng_neutral +
  plot_annotation(title = "No Gratings")
ggsave("C:/MATLAB/exp_1/results/figures/ng_acc.jpg", ng_acc, height = 5)
print(ng_acc)
```

## G Overall (Control vs Migraine)
```{r, message=F, warning=F, echo=F}

tT = "G"

# Valid >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
data <- 
  allGroups |> 
  filter(trialType == tT,
         validity == "valid")

# Set plot contents
g_valid <- 
  ggplot(data, aes(group, percentage)) + 
  # Set Bars
  geom_bar(aes(fill = group),
           position = "dodge",
           stat = "summary",
           fun.y = "mean",
           width = 0.7) +
  # Set whiskers
  stat_boxplot(geom = 'errorbar', 
               width = 0.1, 
               coef = 1.5) +
  # Set plot design
  geom_jitter(#aes(col = id),
              width = 0.3,
              alpha = 0.3) +
  # scale_color_manual(values=c("indianred3", "limegreen", "dodgerblue"))  +
  guides(color = FALSE) +
  geom_boxplot(width = 0.2,
               alpha = 1,
               outlier.shape = NaN) +
  
  # Set mean
  # stat_summary(fun.y = mean, 
  #              geom = "line",
  #              aes(group = 1),
  #              size = 0.8,
  #              colour = "gray50",
  #              show.legend = F) +  
  # stat_summary(fun = mean,
  #              geom = "point",
  #              shape = 16,
  #              size = 1.5,
  #              colour = "black",
  #              show.legend = F)  +
  # Set major labels (title, Y, X axis)
  labs(title = "Valid",
       x = "",
       y = "Accuracy (%)") +
  # Rename each X axis character label
  # scale_x_discrete(limits = c("invalid", "valid"),
  #                  labels = c("Invalid", "Valid")) +
  # Set Y axis range
  ylim(0, 101) +
  # Set colour
  # scale_fill_manual(values=c("coral", "cadetblue1")) +
  # scale_fill_manual(values=c("gray", "gray")) +
  # Plot theme
  theme_bw() +
  # Remove legend
  guides(fill=F)

# Invalid >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
data <-
  allGroups |>
  filter(trialType == tT,
         validity == "invalid")

# Set plot contents
g_invalid <-
  ggplot(data, aes(group, percentage)) +
  # Set Bars
  geom_bar(aes(fill = group),
           position = "dodge",
           stat = "summary",
           fun.y = "mean",
           width = 0.7) +
  # Set whiskers
  stat_boxplot(geom = 'errorbar',
               width = 0.1,
               coef = 1.5) +
  # Set plot design
  geom_jitter(#aes(col = id),
              width = 0.3,
              alpha = 0.3) +
  # scale_color_manual(values=c("indianred3", "limegreen", "dodgerblue"))  +
  guides(color = FALSE) +
  geom_boxplot(width = 0.2,
               alpha = 1,
               outlier.shape = NaN) +

  labs(title = "Invalid",
       x = "",
       y = "") +
  ylim(0, 101) +
  # Plot theme
  theme_bw() +
  # Remove legend
  guides(fill=FALSE)

# Neutral >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
data <-
  allGroups |>
  filter(trialType == tT,
         validity == "neutral")

# Set plot contents
g_neutral <-
  ggplot(data, aes(group, percentage)) +
  # Set Bars
  geom_bar(aes(fill = group),
           position = "dodge",
           stat = "summary",
           fun.y = "mean",
           width = 0.7) +
  # Set whiskers
  stat_boxplot(geom = 'errorbar',
               width = 0.1,
               coef = 1.5) +
  # Set plot design
  geom_jitter(#aes(col = id),
              width = 0.3,
              alpha = 0.3) +
  # scale_color_manual(values=c("indianred3", "limegreen", "dodgerblue"))  +
  guides(color = FALSE) +
  geom_boxplot(width = 0.2,
               alpha = 1,
               outlier.shape = NaN) +
  labs(title = "Neutral",
       x = "",
       y = "") +
  # Set Y axis range
  ylim(0, 101) +
  # Plot theme
  theme_bw() 
  

# mergedC_plot <- plot_grid(noGratRt_C, gratRt_C, labels = c("A", "B"), ncol = 2, nrow = 1)
# title <- ggdraw() + 
#   draw_label(
#     "All Control - RT Correct Detection",
#     fontface = 'bold',
#     x = 0,
#     hjust = 0) +
#   theme(plot.margin = margin(0, 0, 0, 3))
# mergedC_plot <- plot_grid(title, mergedC_plot, ncol = 1, nrow = 2, rel_heights = c(0.05, 1))
# ggsave("C:/MATLAB/exp_1/results/figures/mergedC_plot.png", mergedC_plot, height = 5)
# print(mergedC_plot)

g_acc <- g_valid + g_invalid + g_neutral +
  plot_annotation(title = "Gratings")
ggsave("C:/MATLAB/exp_1/results/figures/g_acc.jpg", g_acc, height = 5)
print(g_acc)
```

# Statistics
```{r, include=F, message=FALSE, warning=FALSE, echo=F}
# Needs raw allGroups
filepath <- "C:/R/exp_1/results/BEH/merged_group_dataset/"
allGroups <- read_csv(paste0(filepath, "allGroups.csv"))
# working data
data <- allGroups
```

## Data Configuration
```{r, message=FALSE, warning=FALSE, echo=F}
data <- 
  data |>
  mutate(group = recode(group, "MA" = "M", # mix migraine groups
                            "MO" = "M"),
         Acc = recode(correctAcc, "correct"=0, "incorrect"=1))  |> 
  # select(id, group, trialType, validity, correctDet, rtDet) |>
  filter(correctDet == "correct", rtDet >0.2)

data$id <- as.factor(data$id)
data$group <- as.factor(data$group)
# data$fixJitData <- as.factor(data$fixJitData)
data$trialType <- as.factor(data$trialType)
data$validity <- as.factor(data$validity)
```

## Full GLMER (Binomial - link: logit) Model
```{r, message=FALSE, warning=FALSE}
acc_model <- 
  glmer(Acc ~ trialType * validity * group + (1|id),
        data = data,
        family = binomial(link = "logit"))
summary(acc_model)
# resid_panel(acc_model, smoother = TRUE, qqbands = TRUE)
```

## Full GLMER (Binomial - link: logit) Model (w/o Group Factor)
```{r, message=FALSE, warning=FALSE}
acc_model_reduced1 <- 
  glmer(Acc ~ trialType * validity + (1|id),
        data = data,
        family = binomial(link = "logit"))
summary(acc_model_reduced1)
# resid_panel(acc_model_reduced1, smoother = TRUE, qqbands = TRUE)
```

# Model Comparison
```{r}
anovaAcc <- 
  anova(acc_model, acc_model_reduced1) |>
  mutate(model = c("Reduced Model", "Full
                   Model"),
         .before = 1) |> 
  kbl() |> 
  kable_classic(full_width = F, 
                html_font = "Cambria")
anovaAcc

```

# Table Comparison
```{r}
# Full Model
mod1 <-
tbl_regression(acc_model,
               intercept = T,
               pvalue_fun = label_style_pvalue(digits =2)) |> 
  # add_global_p() |> 
  bold_p(t = 0.05) |> 
  bold_labels() |> 
  italicize_levels()
# Reduced Model
mod2 <-
  tbl_regression(acc_model_reduced1,
               intercept = T,
               pvalue_fun = label_style_pvalue(digits =2)) |> 
  # add_global_p() |> 
  bold_p(t = 0.05) |> 
  bold_labels() |> 
  italicize_levels()
# Merge Model
tbl_merge(tbls = list(mod1, mod2),
          tab_spanner = c("**Full Model**", "**Reduced Model**")) |> 
  as_gt() |> 
  gt::gtsave(filename = "acc_stats.png",
             path = "C:/MATLAB/exp_1/results/figures")
```































































```{r}
# tes <- mergedC
# 
# tes1 <- 
#   tes |> 
#   mutate(unite(tes, "tt_val", c(trialType, validity), sep = "_"))
```































